\paperTitle

### 2014-05-17 doc/icml2014/discussion.tex

% Bottleneck is key: previous work is preprocessing
Our approach provides consistent estimates for
a family of models in which each hidden variable is a \emph{bottleneck}---that is,
it has three conditionally independent observations.
This bottleneck property of \citet{anandkumar13tensor}
has been exploited in many other contexts,
including Latent Dirichlet Allocation \cite{anandkumar12lda},
mixture of spherical Gaussians \cite{hsu13spherical},
probabilistic grammars \cite{hsu12identifiability},
noisy-or Bayesian networks \cite{halpern13noisyor},
mixture of linear regressions \cite{chaganty13regression},
and others.
Each of these methods can be viewed as ``preprocessing'' the given model into a
form that exposes the bottleneck or tensor factorization structure.
The model parameters correspond directly to the solution of the factorization.

>>>>

% Bottleneck is key: previous work is preprocessing
Our approach provides consistent estimates for
a family of models in which each hidden variable is a \emph{bottleneck}---that is,
it has three conditionally independent observations.
This bottleneck property of \citet{anandkumar13tensor}
has been exploited in many other contexts,
including Latent Dirichlet Allocation \cite{anandkumar12lda},
mixture of spherical Gaussians \cite{hsu13spherical},
probabilistic grammars \cite{hsu12identifiability},
noisy-or Bayesian networks \cite{halpern2013unsupervised},
mixture of linear regressions \cite{chaganty13regression},
and others.
Each of these methods can be viewed as ``preprocessing'' the given model into a
form that exposes the bottleneck or tensor factorization structure.
The model parameters correspond directly to the solution of the factorization.
